Baking the Perfect Cookie

### 2022-12-06 paper.Rmd
Added Table 1.
add ref

---
title: "Baking the Perfect Cookie"
subtitle: "STT 863 Fall 2022"
author: "Benjamin Agyei, Christian Miller, Elliot Shannon, Grayson White"
date: '2022-12-07'
output: pdf_document
fontsize: 12pt
geometry: margin=1in
spacing: double
fig_caption: yes
indent: true
---

@@

Cookies were baked at 350° F for 9 or 12 minutes on a nonstick cookie sheet. A digital timer was used to ensure that each batch of cookies was baked for the appropriate number of minutes.

@@

## References

>>>>

---
title: "Baking the Perfect Cookie"
subtitle: "STT 863 Fall 2022"
author: "Benjamin Agyei, Christian Miller, Elliot Shannon, Grayson White"
date: '2022-12-07'
output: pdf_document
bibliography: references.bib
nocite: '@*'
fontsize: 12pt
geometry: margin=1in
spacing: double
fig_caption: yes
indent: true
---

@@

Cookies were baked at 350° F for 9 or 12 minutes on a nonstick cookie sheet. A digital timer was used to ensure that each batch of cookies was baked for the appropriate number of minutes.
\newline

**Table 1.** Experimental design.
```{r pressure, echo=FALSE, out.width = '50%', fig.align = "center"}
knitr::include_graphics("table.png")
```

@@

\newpage
## References
